Locally-Oriented Programming: A simple programming model for stencil computations

### 2015-01-22 papers/LOPe/program-restructuring.tex
Escaped # symbol.

In Fortran a user can choose between several source-code abstractions for
exploiting parallelism.  The goal of this proposal is to provide tools transform
these abstractions to low-level code for final compilation.  Fortran supports a
data-parallel programming model with array syntax, e.g., C = A + B, where A, B,
C are arrays.  Or the user can explicitly use loop constructs like DO CONCURRENT
to expose parallelism (a Fortran 2008 addition) or by using similar constructs
available in OpenMP like, {\tt #pragma omp parallel for}.

>>>>

In Fortran a user can choose between several source-code abstractions for
exploiting parallelism.  The goal of this proposal is to provide tools transform
these abstractions to low-level code for final compilation.  Fortran supports a
data-parallel programming model with array syntax, e.g., C = A + B, where A, B,
C are arrays.  Or the user can explicitly use loop constructs like DO CONCURRENT
to expose parallelism (a Fortran 2008 addition) or by using similar constructs
available in OpenMP like, {\tt \#pragma omp parallel for}.
